\begin{center}
\large
\textbf{Acknowledgments}
\end{center}

First, I would like to thank my advisor, Dr. Marcia O'Malley. Thank you for taking a chance on a new student you had only met on the phone. And a huge thank you for the amazing amount of help, guidance, and time to work towards my degree. Without Dr. O'Malley, I'm confident I would not have been able to accomplish this degree. Also, I would like to thank the support I received from the entire MAHI lab at Rice. The support you all provided was pivotal through the coursework, but the very valuable friendships that have been formed were an even larger help. 

I would also like to thank all of my co-workers and managers at NASA: Johnson Space Center. To my managers, thank you for helping me set up this opportunity, and allowing me the time needed to attend courses and work on the thesis. For my co-workers, thank you for supporting me and picking up slack when I had to go to meetings, class, and other commitments on campus, I really appreciate it. And of course, thank you to Mason Markee, Ed Herrera, and Anthony Lapp for the inspiration and foundation to begin the work on cycloids. 

And of course, I would like to thank my family. Thank you to my parents who have provided me with so many of the opportunities that allowed me to reach this point. Without your guidance and support, I wouldn't be where I am, and a special thanks for reading all of this and helping find my grammatical errors!
Finally, I would like to thank my fianc\'e, Krista, for her support through this whole process, especially for letting me off the hook for a lot of the wedding planning to finish this thesis. I look forward to repaying the favor for the rest of our lives. 